\section{Conclusion}
\label{section:conlusion}

\subsection{Future Work}
Throughout this paper, we identify many avenues of future work. Sections \ref{section:datasets} and \ref{section:architecture} explain the requirement for large-scale pictoral to geospatial scene-mapping to enable the large scale identification of objects to fuel Gestalt's search. 
Section \ref{section:datasets} highlights the need to develop datasets in dense suburban and urban locations to enable robust testing of ownership assigment process. 
Sections \ref{section:architecture} and \ref{section:implementation} identify the requirement to trial the DVBSCAN algorithm to improve the ownership assignment process, and the need to robustly test the concept mapping proposed using KD-Trees.
Sections \ref{section:implementation} and \ref{section:related} emphasise the need for a usable query interface, and work on pictoral querying offers an interesting direction that enables abstracted user querying and leverages the cognitive advantages of goespatially constructing their query. 
The search component of \textit{GESTALT} needs to be tested at scale. While section \ref{section:implementation} notes that the assumption of only a \textit{last-mile} search allows us to assume small datasets, the performance of the bellingcat tool discussed in section \ref{section:related} shows how quickly performance degrades if not managed well.
Finally, and most importantly, though the psychology literature indicates that the \textit{GESTALT} approach should be helpful to a searcher there is no work actually evaluating this theory, and measuring the extent to which it is helpful. A user study should be prioritised for a fully functional \textit{GESTALT} prototype before it is expanded to full-scale.

\subsection{Conclusion}
The \textit{GESTALT} project aims to reduce the length of time a searcher spends on the \textit{last-mile} of searching for a location. 
It assumes that the \textit{last-mile} is in a constrained geogrpahic region and allows users to search for objects they are likely to remember from candidate locations. 
\textit{GESTALT} is designed to collect geospatial information about locations and objects within geographic regions from open source geospatial and pictoral data. 
It infers the associations between objects visible to searchers in the real world, and the location that they belong to and stores them using bloom filters and KD-Trees for efficient representation and search.
\textit{GESTALT} implements concept mapping to allow a user to query the implicit geospatial relations between objects in candidate locations, leveraging the inherent ordering of the multidimensional KD-Tree data structure for efficient search. 
\textit{GESTALT} demonstrates at a small level, on the Swan Valley wineries dataset that the approach is feasible, and identifies future work in getting it to scale.